---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# R wrapper for multicore Tsne

##Installation

To install the latest version from the github repository, use:
```{r, eval = FALSE}
if(!require(devtools)) install.packages("devtools") # If not already installed
devtools::install_github("RGLab/Rtsne.multicore")
```


##Usage
After installing the package, use the following code to run a simple example (to install, see below).
```{r example, fig.path="tools/"}
library(Rtsne.multicore) # Load package
iris_unique <- unique(iris) # Remove duplicates
mat <- as.matrix(iris_unique[,1:4])
set.seed(42) # Sets seed for reproducibility
tsne_out <- Rtsne.multicore(mat) # Run TSNE
plot(tsne_out$Y,col=iris_unique$Species) # Plot the result
```

##benchmark
```{r}
library(microbenchmark)
library(Rtsne)

microbenchmark(tsne_out <- Rtsne.multicore(mat, num_threads = 4), tsne_out <- Rtsne(mat), times = 10)
```

#Details
This R package offers a wrapper around multicore Barnes-Hut TSNE C++ implementation. Only minor changes were made to the original code to allow it to function as an R package.

#References
[1] L.J.P. van der Maaten and G.E. Hinton. Visualizing High-Dimensional Data Using t-SNE. Journal of Machine Learning Research 9(Nov):2579-2605, 2008.

[2] L.J.P. van der Maaten. Barnes-Hut-SNE. In Proceedings of the International Conference on Learning Representations, 2013.

[3] http://homepage.tudelft.nl/19j49/t-SNE.html

[4] https://github.com/DmitryUlyanov/Multicore-TSNE
